---
title: "ResultsSect"
author: "Freya Acar"
# header-includes:
#   - \usepackage{pdflscape}
#   - \newcommand{\blandscape}{\begin{landscape}}
#   - \newcommand{\elandscape}{\end{landscape}}
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(cache=TRUE)
```

# 

## Descriptives
### Participants
Thirty CW (mean age = 25.80 years, SD = 3.84), 30 CM (mean age = 26.03 years, SD = 5.26), 40 TM (mean age = 24.38 years, SD = 5.35), and 41 TW (mean age = 24.88 years, SD = 6.20) participated in the study. One TW participant was excluded because no results could be extracted from FreeSurfer. Demographics can be observed in Table 1. The sample did not differ significantly in age [F(3, 136) = 0.74, p = 0.528].


### Table with demographic information
```{r read data, warning = FALSE, echo = FALSE}
# Read in data
  data.all <- read.csv("../1.Data/Behzad_all.csv", sep=";", dec=",")
  data.hyp <- read.csv("../1.Data/Behzad_hyp.csv", sep=";", dec=",")
```

```{r table1, warning = FALSE, echo = FALSE}
library(knitr)

dig <- 2 # number of digits after comma
groupn <- c("Group", "CW", "CM", "TM", "TW")
ager <- c("Age", paste(round(mean(data.all[data.all[,2]==1,4]), digits = dig), " ± ", 
                round(sd(data.all[data.all[,2]==1,4]), digits = dig), sep=""),
          paste(round(mean(data.all[data.all[,2]==2,4]), digits = dig), " ± ", 
                round(sd(data.all[data.all[,2]==2,4]), digits = dig), sep=""),
          paste(round(mean(data.all[data.all[,2]==3,4]), digits = dig), " ± ", 
                round(sd(data.all[data.all[,2]==3,4]), digits = dig), sep=""),
          paste(round(mean(data.all[data.all[,2]==4,4]), digits = dig), " ± ", 
                round(sd(data.all[data.all[,2]==4,4]), digits = dig), sep=""))
SESr <- c("SES", paste(round(mean(data.all[data.all[,2]==1,5]), digits = dig), " ± ", 
                round(sd(data.all[data.all[,2]==1,5]), digits = dig), sep=""),
          paste(round(mean(data.all[data.all[,2]==2,5]), digits = dig), " ± ", 
                round(sd(data.all[data.all[,2]==2,5]), digits = dig), sep=""),
          paste(round(mean(data.all[data.all[,2]==3,5]), digits = dig), " ± ", 
                round(sd(data.all[data.all[,2]==3,5]), digits = dig), sep=""),
          paste(round(mean(data.all[data.all[,2]==4,5]), digits = dig), " ± ", 
                round(sd(data.all[data.all[,2]==4,5]), digits = dig), sep=""))
Edr <- c("Education", paste(round(mean(data.all[data.all[,2]==1,6]), digits = dig), " ± ", 
                round(sd(data.all[data.all[,2]==1,6]), digits = dig), sep=""),
          paste(round(mean(data.all[data.all[,2]==2,6]), digits = dig), " ± ", 
                round(sd(data.all[data.all[,2]==2,6]), digits = dig), sep=""),
          paste(round(mean(data.all[data.all[,2]==3,6]), digits = dig), " ± ", 
                round(sd(data.all[data.all[,2]==3,6]), digits = dig), sep=""),
          paste(round(mean(data.all[data.all[,2]==4,6]), digits = dig), " ± ", 
                round(sd(data.all[data.all[,2]==4,6]), digits = dig), sep=""))
Hdr <- c("Handedness", paste(round(mean(data.all[data.all[,2]==1,7]), digits = dig), " ± ", 
                round(sd(data.all[data.all[,2]==1,7]), digits = dig), sep=""),
          paste(round(mean(data.all[data.all[,2]==2,7]), digits = dig), " ± ", 
                round(sd(data.all[data.all[,2]==2,7]), digits = dig), sep=""),
          paste(round(mean(data.all[data.all[,2]==3,7]), digits = dig), " ± ", 
                round(sd(data.all[data.all[,2]==3,7]), digits = dig), sep=""),
          paste(round(mean(data.all[data.all[,2]==4,7]), digits = dig), " ± ", 
                round(sd(data.all[data.all[,2]==4,7]), digits = dig), sep=""))
kable(rbind(groupn, ager, SESr, Edr, Hdr), row.names = FALSE)
```

### Code for demographics
The code can be found in markdown version of this file, it is not printed in the PDF
```{r demogr, warning = FALSE, echo = FALSE, results='hide'}
# Groups
  ng1 <- sum(data.all[,2]==1)
  ng2 <- sum(data.all[,2]==2)
  ng3 <- sum(data.all[,2]==3)
  ng4 <- sum(data.all[,2]==4)
  
  paste("Cisgender women = ", ng1, ", cisgender men = ", ng2, 
        ", transgender men = ", ng3, ", transgender women = ",ng4, sep="")

# Age
  # Cisgender women
  mean(data.all[data.all[,2]==1,4])
  sd(data.all[data.all[,2]==1,4])
  
  # Cisgender men
  mean(data.all[data.all[,2]==2,4])
  sd(data.all[data.all[,2]==2,4])
  
  # Transgender men
  mean(data.all[data.all[,2]==3,4])
  sd(data.all[data.all[,2]==3,4])
  
  # Transgender women
  mean(data.all[data.all[,2]==4,4])
  sd(data.all[data.all[,2]==4,4])
  
  # Difference between groups?
  fit <- lm(formula = data.all[,4] ~ as.factor(data.all[,2]))
  anova(fit)
```

```{r plot age, echo = FALSE, fig.width=6, fig.height=4}
hist(data.all[,4], xlab = "Age", col = "seagreen3", border = "white", 
     main = "Histogram of age distribution", breaks = length(unique(data.all[,4])))
```

## Results
### Repeated measures
Questions: do we want (to account for) a correlation between regions of the same participant?  

First we look at the results for volume. Alle code used to compute this can be found in the markdown version of this document, but is not printed in the pdf.  
We fitted two mixed models. In both models a random intercept for every subject was added, in the second model age and total intracranial volume are added as covariates. An ANOVA is conducted on the results of the mixed models and an FDR-correction is applied over regions. For the regions where a statistically significant difference was found between the groups post-hoc paired comparisons were conducted that are bonferroni-corrected. The results for both models are very similar. The results for the model without covariates are displayed in the table below. If no statistically significant difference is found for a regions "NA" is printed for that region.  


```{r repmes volume, warning = FALSE, include = FALSE, echo = FALSE, results='hide'}
# Libraries
  library(lme4)
  library(lmerTest)
  library(nlme)

# Construct data
  nt <- 2      # number of time points
  nr <- 22     # number of regions
  nsu <- dim(data.hyp)[1]
  
  suc <- rep(1:nsu, each = nt*nr)
  tc <- rep(1:nt, nsu*nr)
  rc <- rep(rep(1:nr, each = nt), nsu)
  gc <- c(rep(c("CW", "CM"), each = (30*nt*nr)), rep(c("TM", "TW"), each = (40*nt*nr)))
  
  j <- 0       # counter for for-loop
  pasteregions <- array(data=NA, dim = nt*nr*nsu)
  for(i in 1:nsu){
    for(r in 1:nr){
      for(t in 1:nt){
        j <- j + 1
        pasteregions[j] <- data.hyp[i,(2+r+(nr*(t-1)))]
      }
    }
  }
  data.lmer <- data.frame(cbind(suc, tc, rc, gc, pasteregions))
  data.lmer$pasteregions <- as.numeric(as.character(data.lmer$pasteregions))

# Fit model
  p.lme <- array(data = NA, dim = nr)
  for(r in 1:nr){
    mf <- lme(pasteregions ~ 1 + gc, random = ~ 1 | suc, data = data.lmer[data.lmer$rc == r,])
    p.lme[r] <- anova(mf)[2,4]
  }
  
# FDR correction
  p.corr <- p.adjust(p.lme, method = "fdr")
  kable(cbind(names(data.hyp[,3:24]), round(p.corr, 3)))
  
# Data with age and total volume
  ac <- rep(data.all[,4], each = nt*nr)
  vc.1 <- rep(data.all[,108], each = nt*nr)
  vc.2 <- rep(data.all[,182], each = nt*nr)
  vc <- vc.1
  for(i in 1:length(vc.1)){
    vc[i] <- ifelse(i%%2==1, vc.1[i], vc.2[i])
  }
  
  data.lmer.cov <- data.frame(cbind(suc, tc, rc, gc, ac, vc, pasteregions))
  data.lmer.cov$pasteregions <- as.numeric(as.character(data.lmer.cov$pasteregions))
  data.lmer.cov$ac <- as.numeric(as.character(data.lmer.cov$ac))
  data.lmer.cov$vc <- as.numeric(as.character(data.lmer.cov$vc))
  
# Fit model
  p.lme.cov <- array(data = NA, dim = nr)
  for(r in 1:nr){
    mf <- lme(pasteregions ~ 1 + gc + ac + vc, random = ~ 1 | suc, data = data.lmer.cov[data.lmer.cov$rc == r,])
    p.lme.cov[r] <- anova(mf)[2,4]
  }
  
# FDR correction
  p.cov.corr <- p.adjust(p.lme.cov, method = "fdr")
  kable(cbind(names(data.hyp[,3:24]), round(p.cov.corr, 3)))
```

```{r posthoc, warning = FALSE, include = FALSE, echo = FALSE, results='hide'}
# create an object with all possible combinations
  allcomb <- combn(c(1:4),2)
  allcomb.txt <- array(data=NA, dim = dim(allcomb)[2])
  labels.g <- c("CW", "CM", "TM", "TW")
  for(i in 1:dim(allcomb)[2]){
    allcomb.txt[i] <- paste(labels.g[allcomb[1,i]], " vs ", labels.g[allcomb[2,i]], sep="")
  }


# create object to save results
  pt <- array(data = NA, dim = c(length(p.corr),dim(allcomb)[2]))
  pt.cov <- array(data = NA, dim = c(length(p.cov.corr),dim(allcomb)[2]))
  pt.corr <- array(data=NA, dim=dim(pt))
  pt.cov.corr <- array(data=NA, dim=dim(pt.cov))
  
# Pair-wise comparisons and correct results
  for(r in 1:nr){
    # general model
    if (p.corr[r] > 0.05) {
        pt[r,] <- rep(NA,dim(allcomb)[2])
    }else{
      for(i in 1:dim(allcomb)[2]){
        pt[r,i] <- unlist(summary(lme(pasteregions ~ 1 + gc, random = ~ 1 | suc, data = data.lmer[data.lmer$rc == r & (data.lmer$gc == labels.g[allcomb[1,i]] | data.lmer$gc == labels.g[allcomb[2,i]]),]))[20])[8]
      }
      pt.corr[r,] <- p.adjust(pt[r,], method = "bonferroni")
    }
    # model with covariates
    if (p.cov.corr[r] > 0.05) {
        pt.cov[r,] <- rep(NA,dim(allcomb)[2])
    }else{
      for(i in 1:dim(allcomb)[2]){
        pt.cov[r,i] <- unlist(summary(lme(pasteregions ~ 1 + gc, random = ~ 1 | suc, data = data.lmer.cov[data.lmer.cov$rc == r & (data.lmer.cov$gc == labels.g[allcomb[1,i]] | data.lmer.cov$gc == labels.g[allcomb[2,i]]),]))[20])[8]
      }
      pt.cov.corr[r,] <- p.adjust(pt.cov[r,], method = "bonferroni")
    }
  }
```

```{r tables, echo = FALSE}
# Model without covariates
  kable(cbind(substring(names(data.hyp[,3:24]), 4), round(p.corr, 3)))
  kable(cbind(c(" ",substring(names(data.hyp[,3:24]), 4)),rbind(c("CW vs CM","CW vs TM","CW vs TW","CM vs TM","CM vs TW","TM vs TW"),round(pt.corr,3))))

# Model with age and total intracranial volume as covariates
  # kable(cbind(c(" ",substring(names(data.hyp[,3:24]), 4)),rbind(c("CW vs CM","CW vs TM","CW vs TW","CM vs TM","CM vs TW","TM vs TW"),round(pt.cov.corr,3))))
```

Then we do the same computations for thickness:  

```{r repmes thickn, warning = FALSE, include = FALSE, echo = FALSE, results='hide'}
# Construct data
  nt <- 2      # number of time points
  nr <- 10     # number of regions
  nsu <- dim(data.hyp)[1]
  
  suc <- rep(1:nsu, each = nt*nr)
  tc <- rep(1:nt, nsu*nr)
  rc <- rep(rep(1:nr, each = nt), nsu)
  gc <- c(rep(c("CW", "CM"), each = (30*nt*nr)), rep(c("TM", "TW"), each = (40*nt*nr)))
  
  j <- 0       # counter for for-loop
  pasteregions <- array(data=NA, dim = nt*nr*nsu)
  for(i in 1:nsu){
    for(r in 1:nr){
      for(t in 1:nt){
        j <- j + 1
        pasteregions[j] <- data.hyp[i,(46+r+(nr*(t-1)))]
      }
    }
  }
  data.lmer.th <- data.frame(cbind(suc, tc, rc, gc, pasteregions))
  data.lmer.th$pasteregions <- as.numeric(as.character(data.lmer.th$pasteregions))

# Fit model
  p.lme.th <- array(data = NA, dim = nr)
  for(r in 1:nr){
    mf <- lme(pasteregions ~ 1 + gc, random = ~ 1 | suc, data = data.lmer.th[data.lmer.th$rc == r,])
    p.lme.th[r] <- anova(mf)[2,4]
  }
  
# FDR correction
  p.corr.th <- p.adjust(p.lme.th, method = "fdr")
  kable(cbind(names(data.hyp[,47:56]), round(p.corr.th, 3)))
  
# Data with age and total volume
  ac <- rep(data.all[,4], each = nt*nr)
  vc.1 <- rep(data.all[,108], each = nt*nr)
  vc.2 <- rep(data.all[,182], each = nt*nr)
  vc <- vc.1
  for(i in 1:length(vc.1)){
    vc[i] <- ifelse(i%%2==1, vc.1[i], vc.2[i])
  }
  
  data.lmer.th.cov <- data.frame(cbind(suc, tc, rc, gc, ac, vc, pasteregions))
  data.lmer.th.cov$pasteregions <- as.numeric(as.character(data.lmer.th.cov$pasteregions))
  data.lmer.th.cov$ac <- as.numeric(as.character(data.lmer.th.cov$ac))
  data.lmer.th.cov$vc <- as.numeric(as.character(data.lmer.th.cov$vc))
  
# Fit model
  p.lme.cov.th <- array(data = NA, dim = nr)
  for(r in 1:nr){
    mf <- lme(pasteregions ~ 1 + gc + ac + vc, random = ~ 1 | suc, data = data.lmer.th.cov[data.lmer.th.cov$rc == r,])
    p.lme.cov.th[r] <- anova(mf)[2,4]
  }
  
# FDR correction
  p.cov.corr.th <- p.adjust(p.lme.cov.th, method = "fdr")
  kable(cbind(names(data.hyp[,47:56]), round(p.cov.corr.th, 3)))
```

```{r posthoc thick, warning = FALSE, include = FALSE, echo = FALSE, results='hide'}
# create object to save results
  pt.th <- array(data = NA, dim = c(length(p.corr.th),dim(allcomb)[2]))
  pt.cov.th <- array(data = NA, dim = c(length(p.cov.corr.th),dim(allcomb)[2]))
  pt.corr.th <- array(data=NA, dim=dim(pt.th))
  pt.cov.corr.th <- array(data=NA, dim=dim(pt.cov.th))
  
# Pair-wise comparisons and correct results
  for(r in 1:nr){
    # general model
    if (p.corr.th[r] > 0.05) {
        pt.th[r,] <- rep(NA,dim(allcomb)[2])
    }else{
      for(i in 1:dim(allcomb)[2]){
        pt.th[r,i] <- unlist(summary(lme(pasteregions ~ 1 + gc, random = ~ 1 | suc, data = data.lmer.th[data.lmer.th$rc == r & (data.lmer.th$gc == labels.g[allcomb[1,i]] | data.lmer.th$gc == labels.g[allcomb[2,i]]),]))[20])[8]
      }
      pt.corr.th[r,] <- p.adjust(pt.th[r,], method = "bonferroni")
    }
    # model with covariates
    if (p.cov.corr.th[r] > 0.05) {
        pt.cov.th[r,] <- rep(NA,dim(allcomb)[2])
    }else{
      for(i in 1:dim(allcomb)[2]){
        pt.cov.th[r,i] <- unlist(summary(lme(pasteregions ~ 1 + gc, random = ~ 1 | suc, data = data.lmer.th.cov[data.lmer.th.cov$rc == r & (data.lmer.th.cov$gc == labels.g[allcomb[1,i]] | data.lmer.th.cov$gc == labels.g[allcomb[2,i]]),]))[20])[8]
      }
      pt.cov.corr.th[r,] <- p.adjust(pt.cov.th[r,], method = "bonferroni")
    }
  }
```


```{r tables thick, echo = FALSE}
# Model without covariates
  kable(cbind(substring(names(data.hyp[,47:56]), 4), round(p.corr.th, 3)))
  kable(cbind(c(" ",substring(names(data.hyp[,47:56]), 4)),rbind(c("CW vs CM","CW vs TM","CW vs TW","CM vs TM","CM vs TW","TM vs TW"),round(pt.corr.th,3))))

# Model with age and total intracranial volume as covariates
  # kable(cbind(c(" ",substring(names(data.hyp[,47:56]), 4)),rbind(c("CW vs CM","CW vs TM","CW vs TW","CM vs TM","CM vs TW","TM vs TW"),round(pt.cov.corr.th,3))))
```

And surface area:  

```{r repmes surfavg, warning = FALSE, include = FALSE, echo = FALSE, results='hide'}
# Construct data
  nt <- 2      # number of time points
  nr <- 10     # number of regions
  nsu <- dim(data.hyp)[1]
  
  suc <- rep(1:nsu, each = nt*nr)
  tc <- rep(1:nt, nsu*nr)
  rc <- rep(rep(1:nr, each = nt), nsu)
  gc <- c(rep(c("CW", "CM"), each = (30*nt*nr)), rep(c("TM", "TW"), each = (40*nt*nr)))
  
  j <- 0       # counter for for-loop
  pasteregions <- array(data=NA, dim = nt*nr*nsu)
  for(i in 1:nsu){
    for(r in 1:nr){
      for(t in 1:nt){
        j <- j + 1
        pasteregions[j] <- data.hyp[i,(66+r+(nr*(t-1)))]
      }
    }
  }
  data.lmer.sa <- data.frame(cbind(suc, tc, rc, gc, pasteregions))
  data.lmer.sa$pasteregions <- as.numeric(as.character(data.lmer.sa$pasteregions))

# Fit model
  p.lme.sa <- array(data = NA, dim = nr)
  for(r in 1:nr){
    mf <- lme(pasteregions ~ 1 + gc, random = ~ 1 | suc, data = data.lmer.sa[data.lmer.sa$rc == r,])
    p.lme.sa[r] <- anova(mf)[2,4]
  }
  
# FDR correction
  p.corr.sa <- p.adjust(p.lme.sa, method = "fdr")
  kable(cbind(names(data.hyp[,67:86]), round(p.corr.sa, 3)))
  
# Data with age and total volume
  ac <- rep(data.all[,4], each = nt*nr)
  vc.1 <- rep(data.all[,108], each = nt*nr)
  vc.2 <- rep(data.all[,182], each = nt*nr)
  vc <- vc.1
  for(i in 1:length(vc.1)){
    vc[i] <- ifelse(i%%2==1, vc.1[i], vc.2[i])
  }
  
  data.lmer.sa.cov <- data.frame(cbind(suc, tc, rc, gc, ac, vc, pasteregions))
  data.lmer.sa.cov$pasteregions <- as.numeric(as.character(data.lmer.sa.cov$pasteregions))
  data.lmer.sa.cov$ac <- as.numeric(as.character(data.lmer.sa.cov$ac))
  data.lmer.sa.cov$vc <- as.numeric(as.character(data.lmer.sa.cov$vc))
  
# Fit model
  p.lme.cov.sa <- array(data = NA, dim = nr)
  for(r in 1:nr){
    mf <- lme(pasteregions ~ 1 + gc + ac + vc, random = ~ 1 | suc, data = data.lmer.sa.cov[data.lmer.sa.cov$rc == r,])
    p.lme.cov.sa[r] <- anova(mf)[2,4]
  }
  
# FDR correction
  p.cov.corr.sa <- p.adjust(p.lme.cov.sa, method = "fdr")
  kable(cbind(names(data.hyp[,67:86]), round(p.cov.corr.sa, 3)))
```

```{r posthoc surfavg, warning = FALSE, include = FALSE, echo = FALSE, results='hide'}
# create object to save results
  pt.sa <- array(data = NA, dim = c(length(p.corr.sa),dim(allcomb)[2]))
  pt.cov.sa <- array(data = NA, dim = c(length(p.cov.corr.sa),dim(allcomb)[2]))
  pt.corr.sa <- array(data=NA, dim=dim(pt.sa))
  pt.cov.corr.sa <- array(data=NA, dim=dim(pt.cov.sa))
  
# Pair-wise comparisons and correct results
  for(r in 1:nr){
    # general model
    if (p.corr.sa[r] > 0.05) {
        pt.sa[r,] <- rep(NA,dim(allcomb)[2])
    }else{
      for(i in 1:dim(allcomb)[2]){
        pt.sa[r,i] <- unlist(summary(lme(pasteregions ~ 1 + gc, random = ~ 1 | suc, data = data.lmer.sa[data.lmer.sa$rc == r & (data.lmer.sa$gc == labels.g[allcomb[1,i]] | data.lmer.sa$gc == labels.g[allcomb[2,i]]),]))[20])[8]
      }
      pt.corr.sa[r,] <- p.adjust(pt.sa[r,], method = "bonferroni")
    }
    # model with covariates
    if (p.cov.corr.sa[r] > 0.05) {
        pt.cov.sa[r,] <- rep(NA,dim(allcomb)[2])
    }else{
      for(i in 1:dim(allcomb)[2]){
        pt.cov.sa[r,i] <- unlist(summary(lme(pasteregions ~ 1 + gc, random = ~ 1 | suc, data = data.lmer.sa.cov[data.lmer.sa.cov$rc == r & (data.lmer.sa.cov$gc == labels.g[allcomb[1,i]] | data.lmer.sa.cov$gc == labels.g[allcomb[2,i]]),]))[20])[8]
      }
      pt.cov.corr.sa[r,] <- p.adjust(pt.cov.sa[r,], method = "bonferroni")
    }
  }
```


```{r tables surfavg, echo = FALSE, warning = FALSE}
# Model without covariates
  kable(cbind(substring(names(data.hyp[,67:(67+nr-1)]), 4), round(p.corr.sa, 3)))
  kable(cbind(c(" ",substring(names(data.hyp[,67:86]), 4)),rbind(c("CW vs CM","CW vs TM","CW vs TW","CM vs TM","CM vs TW","TM vs TW"),round(pt.corr.sa,3))))

# Model with age and total intracranial volume as covariates
  # kable(cbind(c(" ",substring(names(data.hyp[,67:86]), 4)),rbind(c("CW vs CM","CW vs TM","CW vs TW","CM vs TM","CM vs TW","TM vs TW"),round(pt.cov.corr.sa,3))))
```

\newpage

### Compare to results from 1 timepoint
```{r T1, echo = FALSE, warning = FALSE, include = FALSE}
# Volume
  # Dataset
    T1.vol <- data.hyp[,3:24]

  # FDR
    nr <- 22
    p.T1.vol <- array(data=NA, dim = nr)
    for(r in 1:nr){
      p.T1.vol[r] <- unlist(anova(lm(T1.vol[,r] ~ as.factor(data.hyp[,2]))))[9]
    }
    p.T1.vol.corr <- p.adjust(p.T1.vol, method = "fdr")
    
  # Bonferroni
    pt.T1.vol <- array(data = NA, dim = c(nr,dim(allcomb)[2]))
    pt.T1.vol.corr <- array(data = NA, dim = c(nr,dim(allcomb)[2]))
    for(r in 1:nr){
      # general model
      if (p.T1.vol.corr[r] > 0.05) {
          pt.T1.vol[r,] <- rep(NA,dim(allcomb)[2])
      }else{
        for(i in 1:dim(allcomb)[2]){
          pt.T1.vol[r,i] <- unlist(t.test(T1.vol[data.hyp[,2]==allcomb[1,i],r], T1.vol[data.hyp[,2]==allcomb[2,i],r])[3])
        }
        pt.T1.vol.corr[r,] <- p.adjust(pt.T1.vol[r,], method = "bonferroni")
      }
    }

    
# Thickness
  # Dataset
    T1.th <- data.hyp[,47:56]

  # FDR
    nr <- 10
    p.T1.th <- array(data=NA, dim = nr)
    for(r in 1:nr){
      p.T1.th[r] <- unlist(anova(lm(T1.th[,r] ~ as.factor(data.hyp[,2]))))[9]
    }
    p.T1.th.corr <- p.adjust(p.T1.th, method = "fdr")
    
  # Bonferroni
    pt.T1.th <- array(data = NA, dim = c(nr,dim(allcomb)[2]))
    pt.T1.th.corr <- array(data = NA, dim = c(nr,dim(allcomb)[2]))
    for(r in 1:nr){
      # general model
      if (p.T1.th.corr[r] > 0.05) {
          pt.T1.th[r,] <- rep(NA,dim(allcomb)[2])
      }else{
        for(i in 1:dim(allcomb)[2]){
          pt.T1.th[r,i] <- unlist(t.test(T1.th[data.hyp[,2]==allcomb[1,i],r], T1.th[data.hyp[,2]==allcomb[2,i],r])[3])
        }
        pt.T1.th.corr[r,] <- p.adjust(pt.T1.th[r,], method = "bonferroni")
      }
    }

    
# Surface Area
  # Dataset
    T1.sa <- data.hyp[,67:76]

  # FDR
    nr <- 10
    p.T1.sa <- array(data=NA, dim = nr)
    for(r in 1:nr){
      p.T1.sa[r] <- unlist(anova(lm(T1.sa[,r] ~ as.factor(data.hyp[,2]))))[9]
    }
    p.T1.sa.corr <- p.adjust(p.T1.sa, method = "fdr")
    
  # Bonferroni
    pt.T1.sa <- array(data = NA, dim = c(nr,dim(allcomb)[2]))
    pt.T1.sa.corr <- array(data = NA, dim = c(nr,dim(allcomb)[2]))
    for(r in 1:nr){
      # general model
      if (p.T1.sa.corr[r] > 0.05) {
          pt.T1.sa[r,] <- rep(NA,dim(allcomb)[2])
      }else{
        for(i in 1:dim(allcomb)[2]){
          pt.T1.sa[r,i] <- unlist(t.test(T1.sa[data.hyp[,2]==allcomb[1,i],r], T1.sa[data.hyp[,2]==allcomb[2,i],r])[3])
        }
        pt.T1.sa.corr[r,] <- p.adjust(pt.T1.sa[r,], method = "bonferroni")
      }
    }

```

```{r T2, echo = FALSE, warning = FALSE, include = FALSE}
# Volume
  # Dataset
    T2.vol <- data.hyp[,25:46]

  # FDR
    nr <- 22
    p.T2.vol <- array(data=NA, dim = nr)
    for(r in 1:nr){
      p.T2.vol[r] <- unlist(anova(lm(T2.vol[,r] ~ as.factor(data.hyp[,2]))))[9]
    }
    p.T2.vol.corr <- p.adjust(p.T2.vol, method = "fdr")
    
  # Bonferroni
    pt.T2.vol <- array(data = NA, dim = c(nr,dim(allcomb)[2]))
    pt.T2.vol.corr <- array(data = NA, dim = c(nr,dim(allcomb)[2]))
    for(r in 1:nr){
      # general model
      if (p.T2.vol.corr[r] > 0.05) {
          pt.T2.vol[r,] <- rep(NA,dim(allcomb)[2])
      }else{
        for(i in 1:dim(allcomb)[2]){
          pt.T2.vol[r,i] <- unlist(t.test(T2.vol[data.hyp[,2]==allcomb[1,i],r], T2.vol[data.hyp[,2]==allcomb[2,i],r])[3])
        }
        pt.T2.vol.corr[r,] <- p.adjust(pt.T2.vol[r,], method = "bonferroni")
      }
    }

    
# Thickness
  # Dataset
    T2.th <- data.hyp[,57:66]

  # FDR
    nr <- 10
    p.T2.th <- array(data=NA, dim = nr)
    for(r in 1:nr){
      p.T2.th[r] <- unlist(anova(lm(T2.th[,r] ~ as.factor(data.hyp[,2]))))[9]
    }
    p.T2.th.corr <- p.adjust(p.T2.th, method = "fdr")
    
  # Bonferroni
    pt.T2.th <- array(data = NA, dim = c(nr,dim(allcomb)[2]))
    pt.T2.th.corr <- array(data = NA, dim = c(nr,dim(allcomb)[2]))
    for(r in 1:nr){
      # general model
      if (p.T2.th.corr[r] > 0.05) {
          pt.T2.th[r,] <- rep(NA,dim(allcomb)[2])
      }else{
        for(i in 1:dim(allcomb)[2]){
          pt.T2.th[r,i] <- unlist(t.test(T2.th[data.hyp[,2]==allcomb[1,i],r], T2.th[data.hyp[,2]==allcomb[2,i],r])[3])
        }
        pt.T2.th.corr[r,] <- p.adjust(pt.T2.th[r,], method = "bonferroni")
      }
    }

    
# Surface Area
  # Dataset
    T2.sa <- data.hyp[,77:86]

  # FDR
    nr <- 10
    p.T2.sa <- array(data=NA, dim = nr)
    for(r in 1:nr){
      p.T2.sa[r] <- unlist(anova(lm(T2.sa[,r] ~ as.factor(data.hyp[,2]))))[9]
    }
    p.T2.sa.corr <- p.adjust(p.T2.sa, method = "fdr")
    
  # Bonferroni
    pt.T2.sa <- array(data = NA, dim = c(nr,dim(allcomb)[2]))
    pt.T2.sa.corr <- array(data = NA, dim = c(nr,dim(allcomb)[2]))
    for(r in 1:nr){
      # general model
      if (p.T2.sa.corr[r] > 0.05) {
          pt.T2.sa[r,] <- rep(NA,dim(allcomb)[2])
      }else{
        for(i in 1:dim(allcomb)[2]){
          pt.T2.sa[r,i] <- unlist(t.test(T2.sa[data.hyp[,2]==allcomb[1,i],r], T2.sa[data.hyp[,2]==allcomb[2,i],r])[3])
        }
        pt.T2.sa.corr[r,] <- p.adjust(pt.T2.sa[r,], method = "bonferroni")
      }
    }
```

### Volume
Text  
```{r compare V, echo = FALSE, warning = FALSE}
# Volume
  kable(caption = "Comparison volume", rbind(c("Region", "T1", "T2", "Rep Meas"), cbind(substring(names(data.hyp[,3:24]), 4), round(p.T1.vol.corr, 3), round(p.T2.vol.corr, 3), round(p.corr, 3))))
  kable(caption = "Volume: T1", cbind(c(" ",substring(names(data.hyp[,3:24]), 4)),rbind(c("CW vs CM","CW vs TM","CW vs TW","CM vs TM","CM vs TW","TM vs TW"),round(pt.T1.vol.corr,3))))
  kable(caption = "Volume: T2", cbind(c(" ",substring(names(data.hyp[,25:46]), 4)),rbind(c("CW vs CM","CW vs TM","CW vs TW","CM vs TM","CM vs TW","TM vs TW"),round(pt.T2.vol.corr,3))))
```

### Thickness
Text  
```{r compare T, echo = FALSE, warning = FALSE}
# Thickness
  kable(caption = "Comparison thickness", rbind(c("Region", "T1", "T2", "Rep Meas"), cbind(substring(names(data.hyp[,47:56]), 4), round(p.T1.th.corr, 3), round(p.T2.th.corr, 3), round(p.corr.th, 3))))
  kable(caption = "Thickness: T1", cbind(c(" ",substring(names(data.hyp[,47:56]), 4)),rbind(c("CW vs CM","CW vs TM","CW vs TW","CM vs TM","CM vs TW","TM vs TW"),round(pt.T1.th.corr,3))))
  kable(caption = "Thickness: T2", cbind(c(" ",substring(names(data.hyp[,57:66]), 4)),rbind(c("CW vs CM","CW vs TM","CW vs TW","CM vs TM","CM vs TW","TM vs TW"),round(pt.T1.th.corr,3))))
```

### Surface Area
Text  
```{r compare SA, echo = FALSE, warning = FALSE}
# Surface area
  kable(caption = "Comparison surface area", rbind(c("Region", "T1", "T2", "Rep Meas"), cbind(substring(names(data.hyp[,67:76]), 4), round(p.T1.sa.corr, 3), round(p.T2.sa.corr, 3), round(p.corr.sa, 3))))
  kable(caption = "Surface area: T1", cbind(c(" ",substring(names(data.hyp[,67:76]), 4)),rbind(c("CW vs CM","CW vs TM","CW vs TW","CM vs TM","CM vs TW","TM vs TW"),round(pt.T1.sa.corr,3))))
  kable(caption = "Surface area: T2", cbind(c(" ",substring(names(data.hyp[,77:86]), 4)),rbind(c("CW vs CM","CW vs TM","CW vs TW","CM vs TM","CM vs TW","TM vs TW"),round(pt.T1.sa.corr,3))))
```