---
title: "Advantage of two scans in small populations demonstrated with a transgender dataset."
author: "Freya Acar"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(cache=TRUE)
```

# Introduction

# Actual data
```{r ReadData}
# Read in data
data.hyp <- read.csv("../1.Data/Behzad_hyp.csv", sep=";")
data.all <- read.csv("../1.Data/Behzad_all.csv", sep=";")

# Check data
dim(data.hyp)
dim(data.all)
```
## Descriptives
### About the population
Gender
```{r Gender}
ng1 <- sum(data.all[,2]==1)
ng2 <- sum(data.all[,2]==2)
ng3 <- sum(data.all[,2]==3)
ng4 <- sum(data.all[,2]==4)

paste("Cisgender women = ", ng1, ", cisgender men = ", ng2, ", transgender men = ", ng3, ", transgender women = ",ng4, sep="")
```

Age
```{r Age}
summary(data.all[,4])
```

Social-Economic Status
```{r SES}
table(data.all[,5])
```

Level of education
```{r Education}
table(data.all[,6])
```

Handedness
```{r Handedness}
table(data.all[,7])
```

Gender identity
```{r Gender identity}
summary(data.all[,8])
table(data.all[,8])
```

Sexual orientation
```{r Sexual orientation}
summary(data.all[,9])
table(data.all[,9])
```

### Mental illnesses
#### Transgender group
```{r Somatization}
```

```{r OCD}
```


```{r Interpersonal sensitivity}
```


```{r Depression}
```

```{r Anxiety}
```

```{r Hostility}
```

```{r Phobic Anxiety}
```

```{r Paranoia}
```

```{r Psychotism}
```

```{r Global severity}
```

#### Cisgender group
```{r Past psychiatric history}
```
Past psychiatric condition

Past medical condition

### Variables of interest

## Analysis of 1 measurement

## Analysis of the average

## Analysis of 2 measurements

# Simulations
## Intro

## Code
```{r Simulations setup, echo = FALSE, warning = FALSE, include = FALSE}
  # Working directory
```
First we need to define the parameters of our simulations. 
```{r Simulations parameters}
  # variance/sd epsilon
  seps <- 1  

  # Number of simulations
  asim <- 1000

  # Effect size
  delta <- 0.8
  
  # Number of participants
  n <- 30
  n.1 <- n/2      # in the first group
  n.2 <- n/2      # in the second group

  # Level of statistical significance 
  alpha <- 0.05

  # Correlation between first and second measurement
  rho <- seq(0.01,0.99,0.01)
```

Then we prepare objects to store our results
```{r Create objects}
  # Number of simulations
  pow.mean1<-vector("numeric",length(rho))
  pow.mean2<-vector("numeric",length(rho))
  pow.mean3<-vector("numeric",length(rho))
  pow.mean4<-vector("numeric",length(rho))
```

```{r Load libraries, warning=FALSE, echo=FALSE}
  # Libraries
  library(lme4)
  library(lmerTest)
```

```{r Simulations code}
  # Loop over preset correlations between measure 1 and measure 2
  for(i in 1:length(rho)){
    # Create objects to store power in for every simulations
    pow.1<-vector("numeric",asim)
    pow.2<-vector("numeric",asim)
    pow.3<-vector("numeric",asim)
    pow.4<-vector("numeric",asim)
    
    for(k in 1:asim){
        # Scenario 1: lower bound of power curve
        # two groups with equal amount of subjects, groups differ with an effect size delta
          # Construct a vector that determines in which group each subject falls
          x<-c(rep(1,n.1),rep(0,n.2))
          
          # Vector with observations in the set of participants
          y<-rnorm(n,0,seps)       
          # Add an effect size to the first group
          y[1:n.1]<-y[1:n.1]+delta    
        
          # Boolean of whether an effect is detected, this is later used to compute the power
          pow.1[k]<-summary(lm(y~x))$coef[2,4]<alpha
        
        # Scenario 2: upper bound of power curve
        # two groups with equal amount of subjects, twice as many as scenario 1, groups differ with an effect size delta
          # Construct a vector that determines in which group each subject falls
          x2<-c(rep(1,(n.1*2)),rep(0,(n.2*2)))
          
          # Vector with observations in the set of participants
          y2<-rnorm(n*2,0,seps)
          # Add an effect size to the first group
          y2[1:(n.1*2)]<-y2[1:(n.1*2)]+delta
        
          # Boolean of whether an effect is detected, this is later used to compute the power
          pow.2[k]<-summary(lm(y2~x2))$coef[2,4]<alpha

        # Scenario 3: two measurements for every subject, same amount of subjects as in scenario 1
        # two groups with equal amount of subjects, correlation between measurements, groups differ with an effect size delta
          # Construct a vector that determines in which group each subject falls
          x3<-c(rep(1,n.1),rep(0,n.2),rep(1,n.1),rep(0,n.2))
          
          # Vector with first observation of every participant
          y3<-rnorm(n,0,seps)
          # Factor to multiply second set of observations with to obtain results in line with predefined correlation
          alpac<-sqrt(rho[i]^2/(1-rho[i]^2)*seps)
          # Construct second set of observations that are correlated with first set (y3)
          y3.2u<-alpac*y3+rnorm(n)
          y3.2<-y3.2u/sqrt(var(y3.2u))
          # Add effect size to the first group of participants
          y3[1:n.1]<-y3[1:n.1]+delta
          y3.2[1:n.1]<-y3.2[1:n.1]+delta
          # Combine both observations in 1 vector
          y3o<-c(y3,y3.2)
        
          # Define subject numbers
          subject<-rep(1:n,2)
          # Construct mixed model
          mm<-lmer(y3o ~ x3 + (1 | subject))   
          # Boolean of whether an effect is detected, this is later used to compute the power
          pow.3[k]<-summary(mm)$coef[2,5]<alpha
        
        # Scenario 4: What if we work with the average?
          y3m<-(y3+y3.2)/2
          # Boolean of whether an effect is detected, this is later used to compute the power
          pow.4[k]<-summary(lm(y3m~x))$coef[2,4]<alpha
    }
    pow.mean1[i]<-mean(pow.1)
    pow.mean2[i]<-mean(pow.2)
    pow.mean3[i]<-mean(pow.3)
    pow.mean4[i]<-mean(pow.4)
  }
```


## Results
```{r Simulation results}
# power of taking both measures into account
  plot(rho,pow.mean1,ylim=c(0,1), type="l")
  par(new = TRUE)
  plot(rho,pow.mean2,ylim=c(0,1), type="l")
  par(new = TRUE)
  plot(rho,pow.mean3,ylim=c(0,1), type="p", col = "goldenrod3", pch = 2)

# power of using the average
  plot(rho,pow.mean1,ylim=c(0,1), type="l")
  par(new = TRUE)
  plot(rho,pow.mean2,ylim=c(0,1), type="l")
  par(new = TRUE)
  plot(rho,pow.mean3,ylim=c(0,1), type="p", col = "seagreen3", pch = 16)
```

If we overlay both plots we see that there is a lot of overlap. This can also be demonstrated by looking at the results that are exactly the same.
```{r Compare results}
table(pow.mean3==pow.mean4)

# Overlap of both plots
  plot(rho,pow.mean1,ylim=c(0,1), type="l")
  par(new = TRUE)
  plot(rho,pow.mean2,ylim=c(0,1), type="l")
  par(new = TRUE)
  plot(rho,pow.mean3,ylim=c(0,1), type="p", col = "goldenrod3", pch = 2)
  par(new = TRUE)
  plot(rho,pow.mean3,ylim=c(0,1), type="p", col = "seagreen3", pch = 16)
```

# Discussion

```{r temp, echo=FALSE}

```
