---
title: "ResultsSect"
author: "Freya Acar"
date: "4/11/2018"
# header-includes:
#   - \usepackage{pdflscape}
#   - \newcommand{\blandscape}{\begin{landscape}}
#   - \newcommand{\elandscape}{\end{landscape}}
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(cache=TRUE)
```

#

## Descriptives
### Participants
Thirty CW (mean age = 25.80 years, SD = 3.84), 30 CM (mean age = 26.03 years, SD = 5.26), 40 TM (mean age = 24.38 years, SD = 5.35), and 41 TW (mean age = 24.88 years, SD = 6.20) participated in the study. One TW participant was excluded because no results could be extracted from FreeSurfer. Demographics can be observed in Table 1. The sample did not differ significantly in age [F(3, 136) = 0.74, p = 0.528].


### Table with demographic information
```{r read data, warning = FALSE, echo = FALSE}
# Read in data
  data.all <- read.csv("../1.Data/Behzad_all.csv", sep=";", dec=",")
  data.hyp <- read.csv("../1.Data/Behzad_hyp.csv", sep=";", dec=",")
```

```{r table1, warning = FALSE, echo = FALSE}
library(knitr)

dig <- 2 # number of digits after comma
vars <- c("Group", "Age", "SES", "Education", "Handedness")
groupn <- c("CW", "CM", "TM", "TW")
ager <- c(paste(round(mean(data.all[data.all[,2]==1,4]), digits = dig), " ± ", 
                round(sd(data.all[data.all[,2]==1,4]), digits = dig), sep=""),
          paste(round(mean(data.all[data.all[,2]==2,4]), digits = dig), " ± ", 
                round(sd(data.all[data.all[,2]==2,4]), digits = dig), sep=""),
          paste(round(mean(data.all[data.all[,2]==3,4]), digits = dig), " ± ", 
                round(sd(data.all[data.all[,2]==3,4]), digits = dig), sep=""),
          paste(round(mean(data.all[data.all[,2]==4,4]), digits = dig), " ± ", 
                round(sd(data.all[data.all[,2]==4,4]), digits = dig), sep=""))
SESr <- c(paste(round(mean(data.all[data.all[,2]==1,5]), digits = dig), " ± ", 
                round(sd(data.all[data.all[,2]==1,5]), digits = dig), sep=""),
          paste(round(mean(data.all[data.all[,2]==2,5]), digits = dig), " ± ", 
                round(sd(data.all[data.all[,2]==2,5]), digits = dig), sep=""),
          paste(round(mean(data.all[data.all[,2]==3,5]), digits = dig), " ± ", 
                round(sd(data.all[data.all[,2]==3,5]), digits = dig), sep=""),
          paste(round(mean(data.all[data.all[,2]==4,5]), digits = dig), " ± ", 
                round(sd(data.all[data.all[,2]==4,5]), digits = dig), sep=""))
Edr <- c(paste(round(mean(data.all[data.all[,2]==1,6]), digits = dig), " ± ", 
                round(sd(data.all[data.all[,2]==1,6]), digits = dig), sep=""),
          paste(round(mean(data.all[data.all[,2]==2,6]), digits = dig), " ± ", 
                round(sd(data.all[data.all[,2]==2,6]), digits = dig), sep=""),
          paste(round(mean(data.all[data.all[,2]==3,6]), digits = dig), " ± ", 
                round(sd(data.all[data.all[,2]==3,6]), digits = dig), sep=""),
          paste(round(mean(data.all[data.all[,2]==4,6]), digits = dig), " ± ", 
                round(sd(data.all[data.all[,2]==4,6]), digits = dig), sep=""))
Hdr <- c(paste(round(mean(data.all[data.all[,2]==1,7]), digits = dig), " ± ", 
                round(sd(data.all[data.all[,2]==1,7]), digits = dig), sep=""),
          paste(round(mean(data.all[data.all[,2]==2,7]), digits = dig), " ± ", 
                round(sd(data.all[data.all[,2]==2,7]), digits = dig), sep=""),
          paste(round(mean(data.all[data.all[,2]==3,7]), digits = dig), " ± ", 
                round(sd(data.all[data.all[,2]==3,7]), digits = dig), sep=""),
          paste(round(mean(data.all[data.all[,2]==4,7]), digits = dig), " ± ", 
                round(sd(data.all[data.all[,2]==4,7]), digits = dig), sep=""))
kable(cbind(vars, rbind(groupn, ager, SESr, Edr, Hdr)))
```

### Code for demographics
The code can be found in markdown version of this file, it is not printed on the PDF
```{r demogr, warning = FALSE, echo = FALSE, results='hide'}
# Groups
  ng1 <- sum(data.all[,2]==1)
  ng2 <- sum(data.all[,2]==2)
  ng3 <- sum(data.all[,2]==3)
  ng4 <- sum(data.all[,2]==4)
  
  paste("Cisgender women = ", ng1, ", cisgender men = ", ng2, 
        ", transgender men = ", ng3, ", transgender women = ",ng4, sep="")

# Age
  # Cisgender women
  mean(data.all[data.all[,2]==1,4])
  sd(data.all[data.all[,2]==1,4])
  
  # Cisgender men
  mean(data.all[data.all[,2]==2,4])
  sd(data.all[data.all[,2]==2,4])
  
  # Transgender men
  mean(data.all[data.all[,2]==3,4])
  sd(data.all[data.all[,2]==3,4])
  
  # Transgender women
  mean(data.all[data.all[,2]==4,4])
  sd(data.all[data.all[,2]==4,4])
  
  # Difference between groups?
  fit <- lm(formula = data.all[,4] ~ as.factor(data.all[,2]))
  anova(fit)
```

Plot with ages
```{r plot age, echo = FALSE}
hist(data.all[,4], xlab = "Age", col = "seagreen3", border = "white", 
     main = "Histogram of age distribution", breaks = length(unique(data.all[,4])))
```

## Results
### Repeated measures
Questions: do we want a correlation between regions of the same participant?  

Everything for volume is computed here:  
```{r repmes volume, warning = FALSE, include = FALSE, echo = FALSE, results='hide'}
# Libraries
  library(lme4)
  library(lmerTest)
  library(nlme)

# Construct data
  nt <- 2      # number of time points
  nr <- 22     # number of regions
  nsu <- dim(data.hyp)[1]
  
  suc <- rep(1:nsu, each = nt*nr)
  tc <- rep(1:nt, nsu*nr)
  rc <- rep(rep(1:nr, each = nt), nsu)
  gc <- c(rep(c("CW", "CM"), each = (30*nt*nr)), rep(c("TM", "TW"), each = (40*nt*nr)))
  
  j <- 0       # counter for for-loop
  pasteregions <- array(data=NA, dim = nt*nr*nsu)
  for(i in 1:nsu){
    for(r in 1:nr){
      for(t in 1:nt){
        j <- j + 1
        pasteregions[j] <- data.hyp[i,(2+r+(nr*(t-1)))]
      }
    }
  }
  data.lmer <- data.frame(cbind(suc, tc, rc, gc, pasteregions))
  data.lmer$pasteregions <- as.numeric(as.character(data.lmer$pasteregions))

# Fit model
  p.lme <- array(data = NA, dim = nr)
  for(r in 1:nr){
    mf <- lme(pasteregions ~ 1 + gc, random = ~ 1 | suc, data = data.lmer[data.lmer$rc == r,])
    p.lme[r] <- anova(mf)[2,4]
  }
  
# FDR correction
  p.corr <- p.adjust(p.lme, method = "fdr")
  kable(cbind(names(data.hyp[,3:24]), round(p.corr, 3)))
  
# Data with age and total volume
  ac <- rep(data.all[,4], each = nt*nr)
  vc.1 <- rep(data.all[,108], each = nt*nr)
  vc.2 <- rep(data.all[,182], each = nt*nr)
  vc <- vc.1
  for(i in 1:length(vc.1)){
    vc[i] <- ifelse(i%%2==1, vc.1[i], vc.2[i])
  }
  
  data.lmer.cov <- data.frame(cbind(suc, tc, rc, gc, ac, vc, pasteregions))
  data.lmer.cov$pasteregions <- as.numeric(as.character(data.lmer.cov$pasteregions))
  data.lmer.cov$ac <- as.numeric(as.character(data.lmer.cov$ac))
  data.lmer.cov$vc <- as.numeric(as.character(data.lmer.cov$vc))
  
# Fit model
  p.lme.cov <- array(data = NA, dim = nr)
  for(r in 1:nr){
    mf <- lme(pasteregions ~ 1 + gc + ac + vc, random = ~ 1 | suc, data = data.lmer.cov[data.lmer.cov$rc == r,])
    p.lme.cov[r] <- anova(mf)[2,4]
  }
  
# FDR correction
  p.cov.corr <- p.adjust(p.lme.cov, method = "fdr")
  kable(cbind(names(data.hyp[,3:24]), round(p.cov.corr, 3)))
```
### Post-hoc tests
```{r posthoc, warning = FALSE, include = FALSE, echo = FALSE, results='hide'}
# create an object with all possible combinations
  allcomb <- combn(c(1:4),2)
  allcomb.txt <- array(data=NA, dim = dim(allcomb)[2])
  labels.g <- c("CW", "CM", "TM", "TW")
  for(i in 1:dim(allcomb)[2]){
    allcomb.txt[i] <- paste(labels.g[allcomb[1,i]], " vs ", labels.g[allcomb[2,i]], sep="")
  }


# create object to save results
  pt <- array(data = NA, dim = c(length(p.corr),dim(allcomb)[2]))
  pt.cov <- array(data = NA, dim = c(length(p.cov.corr),dim(allcomb)[2]))
  pt.corr <- array(data=NA, dim=dim(pt))
  pt.cov.corr <- array(data=NA, dim=dim(pt.cov))
  
# T-tests and correct results
  for(r in 1:nr){
    # general model
    if (p.corr[r] > 0.05) {
        pt[r,] <- rep(NA,dim(allcomb)[2])
    }else{
      for(i in 1:dim(allcomb)[2]){
        pt[r,i] <- unlist(t.test(data.lmer[data.lmer$rc==r & data.lmer$gc==labels.g[allcomb[1,i]],5], data.lmer[data.lmer$rc==r & data.lmer$gc==labels.g[allcomb[2,i]],5])[3])
      }
      pt.corr[r,] <- p.adjust(pt[r,], method = "bonferroni")
    }
    # model with covariates
    if (p.cov.corr[r] > 0.05) {
        pt.cov[r,] <- rep(NA,dim(allcomb)[2])
    }else{
      for(i in 1:dim(allcomb)[2]){
        pt.cov[r,i] <- unlist(t.test(data.lmer.cov[data.lmer.cov$rc==r & data.lmer.cov$gc==labels.g[allcomb[1,i]],7], data.lmer.cov[data.lmer.cov$rc==r & data.lmer.cov$gc==labels.g[allcomb[2,i]],7])[3])
      }
      pt.cov.corr[r,] <- p.adjust(pt.cov[r,], method = "bonferroni")
    }
  }
```

In the tables the results for the model with and without covariates are displayed.   

```{r tables, echo = FALSE}
# Model without covariates
  kable(cbind(c(" ",substring(names(data.hyp[,3:24]), 4)),rbind(c("CW vs CM","CW vs TM","CW vs TW","CM vs TM","CM vs TW","TM vs TW"),round(pt.corr,3))))

# Model with age and total intracranial volume as covariates
  kable(cbind(c(" ",substring(names(data.hyp[,3:24]), 4)),rbind(c("CW vs CM","CW vs TM","CW vs TW","CM vs TM","CM vs TW","TM vs TW"),round(pt.cov.corr,3))))
```

Then we do the same computations for thickness:  

```{r repmes thickn, warning = FALSE, include = FALSE, echo = FALSE, results='hide'}
# Construct data
  nt <- 2      # number of time points
  nr <- 10     # number of regions
  nsu <- dim(data.hyp)[1]
  
  suc <- rep(1:nsu, each = nt*nr)
  tc <- rep(1:nt, nsu*nr)
  rc <- rep(rep(1:nr, each = nt), nsu)
  gc <- c(rep(c("CW", "CM"), each = (30*nt*nr)), rep(c("TM", "TW"), each = (40*nt*nr)))
  
  j <- 0       # counter for for-loop
  pasteregions <- array(data=NA, dim = nt*nr*nsu)
  for(i in 1:nsu){
    for(r in 1:nr){
      for(t in 1:nt){
        j <- j + 1
        pasteregions[j] <- data.hyp[i,(46+r+(nr*(t-1)))]
      }
    }
  }
  data.lmer.th <- data.frame(cbind(suc, tc, rc, gc, pasteregions))
  data.lmer.th$pasteregions <- as.numeric(as.character(data.lmer.th$pasteregions))

# Fit model
  p.lme.th <- array(data = NA, dim = nr)
  for(r in 1:nr){
    mf <- lme(pasteregions ~ 1 + gc, random = ~ 1 | suc, data = data.lmer.th[data.lmer.th$rc == r,])
    p.lme.th[r] <- anova(mf)[2,4]
  }
  
# FDR correction
  p.corr.th <- p.adjust(p.lme.th, method = "fdr")
  kable(cbind(names(data.hyp[,47:56]), round(p.corr.th, 3)))
  
# Data with age and total volume
  ac <- rep(data.all[,4], each = nt*nr)
  vc.1 <- rep(data.all[,108], each = nt*nr)
  vc.2 <- rep(data.all[,182], each = nt*nr)
  vc <- vc.1
  for(i in 1:length(vc.1)){
    vc[i] <- ifelse(i%%2==1, vc.1[i], vc.2[i])
  }
  
  data.lmer.th.cov <- data.frame(cbind(suc, tc, rc, gc, ac, vc, pasteregions))
  data.lmer.th.cov$pasteregions <- as.numeric(as.character(data.lmer.th.cov$pasteregions))
  data.lmer.th.cov$ac <- as.numeric(as.character(data.lmer.th.cov$ac))
  data.lmer.th.cov$vc <- as.numeric(as.character(data.lmer.th.cov$vc))
  
# Fit model
  p.lme.cov.th <- array(data = NA, dim = nr)
  for(r in 1:nr){
    mf <- lme(pasteregions ~ 1 + gc + ac + vc, random = ~ 1 | suc, data = data.lmer.th.cov[data.lmer.th.cov$rc == r,])
    p.lme.cov.th[r] <- anova(mf)[2,4]
  }
  
# FDR correction
  p.cov.corr.th <- p.adjust(p.lme.cov.th, method = "fdr")
  kable(cbind(names(data.hyp[,47:56]), round(p.cov.corr.th, 3)))
```

### Post-hoc tests
```{r posthoc thick, warning = FALSE, include = FALSE, echo = FALSE, results='hide'}
# create object to save results
  pt.th <- array(data = NA, dim = c(length(p.corr.th),dim(allcomb)[2]))
  pt.cov.th <- array(data = NA, dim = c(length(p.cov.corr.th),dim(allcomb)[2]))
  pt.corr.th <- array(data=NA, dim=dim(pt.th))
  pt.cov.corr.th <- array(data=NA, dim=dim(pt.cov.th))
  
# T-tests and correct results
  for(r in 1:nr){
    # general model
    if (p.corr.th[r] > 0.05) {
        pt.th[r,] <- rep(NA,dim(allcomb)[2])
    }else{
      for(i in 1:dim(allcomb)[2]){
        pt.th[r,i] <- unlist(t.test(data.lmer.th[data.lmer.th$rc==r & data.lmer.th$gc==labels.g[allcomb[1,i]],5], data.lmer.th[data.lmer.th$rc==r & data.lmer.th$gc==labels.g[allcomb[2,i]],5])[3])
      }
      pt.corr.th[r,] <- p.adjust(pt.th[r,], method = "bonferroni")
    }
    # model with covariates
    if (p.cov.corr.th[r] > 0.05) {
        pt.cov.th[r,] <- rep(NA,dim(allcomb)[2])
    }else{
      for(i in 1:dim(allcomb)[2]){
        pt.cov.th[r,i] <- unlist(t.test(data.lmer.cov.th[data.lmer.cov.th$rc==r & data.lmer.cov.th$gc==labels.g[allcomb[1,i]],7], data.lmer.cov.th[data.lmer.cov.th$rc==r & data.lmer.cov.th$gc==labels.g[allcomb[2,i]],7])[3])
      }
      pt.cov.corr.th[r,] <- p.adjust(pt.cov.th[r,], method = "bonferroni")
    }
  }
```

In the tables the results for the model with and without covariates are displayed.   

```{r tables thick, echo = FALSE}
# Model without covariates
  kable(cbind(c(" ",substring(names(data.hyp[,47:56]), 4)),rbind(c("CW vs CM","CW vs TM","CW vs TW","CM vs TM","CM vs TW","TM vs TW"),round(pt.corr.th,3))))

# Model with age and total intracranial volume as covariates
  kable(cbind(c(" ",substring(names(data.hyp[,47:56]), 4)),rbind(c("CW vs CM","CW vs TM","CW vs TW","CM vs TM","CM vs TW","TM vs TW"),round(pt.cov.corr.th,3))))
```

And surface area:  

```{r repmes surfavg, warning = FALSE, include = FALSE, echo = FALSE, results='hide'}
# Construct data
  nt <- 2      # number of time points
  nr <- 10     # number of regions
  nsu <- dim(data.hyp)[1]
  
  suc <- rep(1:nsu, each = nt*nr)
  tc <- rep(1:nt, nsu*nr)
  rc <- rep(rep(1:nr, each = nt), nsu)
  gc <- c(rep(c("CW", "CM"), each = (30*nt*nr)), rep(c("TM", "TW"), each = (40*nt*nr)))
  
  j <- 0       # counter for for-loop
  pasteregions <- array(data=NA, dim = nt*nr*nsu)
  for(i in 1:nsu){
    for(r in 1:nr){
      for(t in 1:nt){
        j <- j + 1
        pasteregions[j] <- data.hyp[i,(66+r+(nr*(t-1)))]
      }
    }
  }
  data.lmer.sa <- data.frame(cbind(suc, tc, rc, gc, pasteregions))
  data.lmer.sa$pasteregions <- as.numeric(as.character(data.lmer.sa$pasteregions))

# Fit model
  p.lme.sa <- array(data = NA, dim = nr)
  for(r in 1:nr){
    mf <- lme(pasteregions ~ 1 + gc, random = ~ 1 | suc, data = data.lmer.sa[data.lmer.sa$rc == r,])
    p.lme.sa[r] <- anova(mf)[2,4]
  }
  
# FDR correction
  p.corr.sa <- p.adjust(p.lme.sa, method = "fdr")
  kable(cbind(names(data.hyp[,67:86]), round(p.corr.sa, 3)))
  
# Data with age and total volume
  ac <- rep(data.all[,4], each = nt*nr)
  vc.1 <- rep(data.all[,108], each = nt*nr)
  vc.2 <- rep(data.all[,182], each = nt*nr)
  vc <- vc.1
  for(i in 1:length(vc.1)){
    vc[i] <- ifelse(i%%2==1, vc.1[i], vc.2[i])
  }
  
  data.lmer.sa.cov <- data.frame(cbind(suc, tc, rc, gc, ac, vc, pasteregions))
  data.lmer.sa.cov$pasteregions <- as.numeric(as.character(data.lmer.sa.cov$pasteregions))
  data.lmer.sa.cov$ac <- as.numeric(as.character(data.lmer.sa.cov$ac))
  data.lmer.sa.cov$vc <- as.numeric(as.character(data.lmer.sa.cov$vc))
  
# Fit model
  p.lme.cov.sa <- array(data = NA, dim = nr)
  for(r in 1:nr){
    mf <- lme(pasteregions ~ 1 + gc + ac + vc, random = ~ 1 | suc, data = data.lmer.sa.cov[data.lmer.sa.cov$rc == r,])
    p.lme.cov.sa[r] <- anova(mf)[2,4]
  }
  
# FDR correction
  p.cov.corr.sa <- p.adjust(p.lme.cov.sa, method = "fdr")
  kable(cbind(names(data.hyp[,67:86]), round(p.cov.corr.sa, 3)))
```

### Post-hoc tests
```{r posthoc surfavg, warning = FALSE, include = FALSE, echo = FALSE, results='hide'}
# create object to save results
  pt.sa <- array(data = NA, dim = c(length(p.corr.sa),dim(allcomb)[2]))
  pt.cov.sa <- array(data = NA, dim = c(length(p.cov.corr.sa),dim(allcomb)[2]))
  pt.corr.sa <- array(data=NA, dim=dim(pt.sa))
  pt.cov.corr.sa <- array(data=NA, dim=dim(pt.cov.sa))
  
# T-tests and correct results
  for(r in 1:nr){
    # general model
    if (p.corr.sa[r] > 0.05) {
        pt.sa[r,] <- rep(NA,dim(allcomb)[2])
    }else{
      for(i in 1:dim(allcomb)[2]){
        pt.sa[r,i] <- unlist(t.test(data.lmer.sa[data.lmer.sa$rc==r & data.lmer.sa$gc==labels.g[allcomb[1,i]],5], data.lmer.sa[data.lmer.sa$rc==r & data.lmer.sa$gc==labels.g[allcomb[2,i]],5])[3])
      }
      pt.corr.sa[r,] <- p.adjust(pt.sa[r,], method = "bonferroni")
    }
    # model with covariates
    if (p.cov.corr.sa[r] > 0.05) {
        pt.cov.sa[r,] <- rep(NA,dim(allcomb)[2])
    }else{
      for(i in 1:dim(allcomb)[2]){
        pt.cov.sa[r,i] <- unlist(t.test(data.lmer.sa.cov[data.lmer.sa.cov$rc==r & data.lmer.sa.cov$gc==labels.g[allcomb[1,i]],7], data.lmer.sa.cov[data.lmer.sa.cov$rc==r & data.lmer.sa.cov$gc==labels.g[allcomb[2,i]],7])[3])
      }
      pt.cov.corr.sa[r,] <- p.adjust(pt.cov.sa[r,], method = "bonferroni")
    }
  }
```

In the tables the results for the model with and without covariates are displayed.   

```{r tables surfavg, echo = FALSE}
# Model without covariates
  kable(cbind(c(" ",substring(names(data.hyp[,67:86]), 4)),rbind(c("CW vs CM","CW vs TM","CW vs TW","CM vs TM","CM vs TW","TM vs TW"),round(pt.corr.sa,3))))

# Model with age and total intracranial volume as covariates
  kable(cbind(c(" ",substring(names(data.hyp[,67:86]), 4)),rbind(c("CW vs CM","CW vs TM","CW vs TW","CM vs TM","CM vs TW","TM vs TW"),round(pt.cov.corr.sa,3))))
```

<!-- In the end we can construct a table that shows the results of all three measures together   -->
<!-- \newpage -->
<!-- \blandscape -->

<!-- ```{r general table} -->
<!-- nameregions <- c("Groups", "Measure", "Fusiform L", "Fusiform R", "Inferiorparietal L", "Inferiorparietal R", "Postcentral L", "Postcentral R", "Precentral L", "Precentral R", "Frontal Pole L", "Frontal Pole R", "Cerebellum WM L", "Cerebellum WM R", "Cerebellum Cortex L", "Cerebellum Cortex R", "Thalamus L", "Thalamus R", "Caudate L", "Caudate R", "Putamen L", "Putamen R", "Accumbens L", "Accumbens R") -->
<!-- c1.1 <- c(groupn[allcomb[1,1]], "V") -->
<!-- c1.2 <- c(" vs ", "T") -->
<!-- c1.3 <- c(groupn[allcomb[2,1]], "SA") -->
<!-- c2.1 <- c(groupn[allcomb[1,2]], "V") -->
<!-- c2.2 <- c(" vs ", "T") -->
<!-- c2.3 <- c(groupn[allcomb[2,2]], "SA") -->
<!-- c3.1 <- c(groupn[allcomb[1,3]], "V") -->
<!-- c3.2 <- c(" vs ", "T") -->
<!-- c3.3 <- c(groupn[allcomb[2,3]], "SA") -->
<!-- c4.1 <- c(groupn[allcomb[1,4]], "V") -->
<!-- c4.2 <- c(" vs ", "T") -->
<!-- c4.3 <- c(groupn[allcomb[2,4]], "SA") -->
<!-- c5.1 <- c(groupn[allcomb[1,5]], "V") -->
<!-- c5.2 <- c(" vs ", "T") -->
<!-- c5.3 <- c(groupn[allcomb[2,5]], "SA") -->
<!-- c6.1 <- c(groupn[allcomb[1,6]], "V") -->
<!-- c6.2 <- c(" vs ", "T") -->
<!-- c6.3 <- c(groupn[allcomb[2,6]], "SA") -->
<!-- kable(cbind(c1.1, c1.2, c1.3, c2.1, c2.2, c2.3, c3.1, c3.2, c3.3, c4.1, c4.2, c4.3, c5.1, c5.2, c5.3, c6.1, c6.2, c6.3)) -->
<!-- ``` -->
<!-- \elandscape -->