---
title: "ResultsT"
author: "Freya Acar"
date: "4/11/2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(cache=TRUE)
```

# Overview
1. [Introduction](#introduction)
2. [Startup](#startup)
3. [Descriptives](#descriptives)
4. [Analysis](#ansect)
5. [Posthoc](#posthocsect)
6. [Correlations between T1 and T2](#correlations)
7. [Discussion](#discussion)

\newpage

## Introduction <a name="introduction"></a>  
We have a dataset where FreeSurfer was used to determine cortical and subcortical brain anatomy in cis- and transgender population. For every participant two scans were administered (T1 and T2) and an average of both scans was computed. In this report we analyze the data from one scan and the average of both scans. Later on we show the advantage and increase in power obtained by admninistering 2 scans.  
One participant (P22) was removed from the analysis because no anatomical data was available for this participant.  

\newpage
  
## Startup <a name="startup"></a>  
We first read in the data. In data.all all available measurements are stored (descriptive and anatomical) while in data.hyp the anatomical results for every region of interest stored. Both files contain data of T1, T2 and the average. 
```{r ReadData}
# Libraries
library(knitr)

# Read in data
data.all <- read.csv("../1.Data/Behzad_all.csv", sep=";", dec=",")
data.hyp <- read.csv("../1.Data/Behzad_hyp.csv", sep=";", dec=",")

# Check data
dim(data.hyp)
dim(data.all)
```

The regions we are interested in are the cerebellum, caudate, putamen, nucleus accumenbens, thalamus, fusiform, pre-central gyrus, post-central gyrus, frontal poles and inferior parietal gyrus. Here we list the variables we selected from FreeSurfer that comply with these regions.
```{r roi}
# Regions of interest
names(data.hyp[,47:68])
```

\newpage

## Descriptives <a name="descriptives"></a>
In this section population parameters are presented. 

###Gender
There were 60 cisgender and 80 transgender participants. One participant (P22) was removed from the analysis because no anatomical data was available for this participant. 
```{r Gender, out.width='.49\\linewidth', fig.width=3, fig.height=3,fig.show='hold',fig.align='center'}
ng1 <- sum(data.all[,2]==1)
ng2 <- sum(data.all[,2]==2)
ng3 <- sum(data.all[,2]==3)
ng4 <- sum(data.all[,2]==4)

paste("Cisgender women = ", ng1, ", cisgender men = ", ng2, 
      ", transgender men = ", ng3, ", transgender women = ",ng4, sep="")

hist(data.all[,2], breaks = 5, xlab = "Gender", xaxt = "n", col = "seagreen3", 
     border = "white", main = "Frequency of gender")
axis(1,at=c(1:4),labels=c("CW", "CM", "TM", "TW"))
```

###Age
```{r Age}
summary(data.all[,4])

hist(data.all[,4], xlab = "Age", col = "seagreen3", border = "white", 
     main = "Histogram of age distribution", breaks = length(unique(data.all[,4])))
```

Age of the participants ranged from 16 to 44. If we look at the distribution of age in the cis- and transgender group we see that the range is similar in both groups.

```{r agediff}
# Cisgender women
mean(data.all[data.all[,2]==1,4])
sd(data.all[data.all[,2]==1,4])

# Cisgender men
mean(data.all[data.all[,2]==2,4])
sd(data.all[data.all[,2]==2,4])

# Transgender men
mean(data.all[data.all[,2]==3,4])
sd(data.all[data.all[,2]==3,4])

# Transgender women
mean(data.all[data.all[,2]==4,4])
sd(data.all[data.all[,2]==4,4])
```

\newpage

## Analysis of the data <a name="ansect"></a>
### Analysis of one measurement
We compute an ANOVA on all hypothesis regions with the data from T1.
```{r onemeas, out.width='.49\\linewidth', fig.width=4, fig.height=3,fig.show='hold',fig.align='center'}
bg.one <- 3
nd.one <- 24
ln <- nd.one-bg.one
fac <- c(rep("CW",30), rep("CM",30), rep("TM",40), rep("TW",40))  # factor for participant group

# Object to save p-values of ANOVA
pan.one <- array(data=NA, dim = ln)

# Compute ANOVA for every predictor and save p-value
for(i in bg.one:nd.one){
  tempan <- aov(data.hyp[,i] ~ as.factor(data.hyp[,2]))
  pan.one[i-bg.one+1] <- unlist(summary(tempan))[9]
}

# FDR correction on p-values to correct for multiple testing
pancorr.one <- p.adjust(pan.one, method = "fdr")
sum(pancorr.one < 0.05)

kable(cbind(names(data.hyp[,bg.one:nd.one]), round(pancorr.one, 3)))
```

\newpage

### Analysis of the average
We computed the same ANOVA on the average.
```{r average, out.width='.49\\linewidth', fig.width=4, fig.height=3,fig.show='hold',fig.align='center'}
bg.avg <- 47
nd.avg <- 68
ln <- nd.avg-bg.avg+1
fac <- c(rep("CW",30), rep("CM",30), rep("TM",40), rep("TW",40))  # factor for participant group

# Object to save p-values of ANOVA
pan.avg <- array(data=NA, dim = ln)

# Compute ANOVA for every predictor and save p-value
for(i in bg.avg:nd.avg){
  tempan <- aov(data.hyp[,i] ~ as.factor(data.hyp[,2]))
  pan.avg[i-bg.avg+1] <- unlist(summary(tempan))[9]
}

# FDR correction on p-values to correct for multiple testing
pancorr.avg <- p.adjust(pan.avg, method = "fdr")
sum(pancorr.avg < 0.05)

kable(cbind(names(data.hyp[,bg.avg:nd.avg]), round(pancorr.avg, 3)))
```

Why are there less regions for which the difference is statistically significant when the average is used compared to when one measure is used? 
To investigate this we look at the difference between the boxplots for one statistically significant region.
```{r diff, out.width='.49\\linewidth', fig.width=4, fig.height=3,fig.show='hold',fig.align='center'}
boxplot(data.hyp[,22] ~ fac, main = names(data.hyp)[26])
boxplot(data.hyp[,66] ~ fac, main = names(data.hyp)[78])

for(i in bg.one:nd.one){
  # construct boxplot for every region
  boxplot(data.hyp[,i] ~ fac, main = names(data.hyp)[i])
  boxplot(data.hyp[,i + 44] ~ fac, main = names(data.hyp)[i + 44])
}
```

\newpage

## Post-hoc tests <a name="posthocsect"></a>
We conduct post-hoc t-tests on the statistically significant regions to determine which group differences cause the effect. The p-values are uncorrected at this point and I computed them for every region. 
```{r posthoc}
# create an object with all possible combinations
  allcomb <- combn(c(1:4),2)
  allcomb.txt <- array(data=NA, dim = dim(allcomb)[2])
  labels.g <- c("CW", "CM", "TM", "TW")
  for(i in 1:dim(allcomb)[2]){
    allcomb.txt[i] <- paste(labels.g[allcomb[1,i]], " vs ", labels.g[allcomb[2,i]], sep="")
  }
  

# create object to save results
  pt.one <- array(data = NA, dim = c(length(pan.one),dim(allcomb)[2]))
  pt.avg <- array(data = NA, dim = c(length(pan.avg),dim(allcomb)[2]))

# Left Cerebellum White Matter
  # 1 measure
  bg.one <- 3
  nd.one <- 24
  pt.corr.one <- array(data=NA, dim=dim(pt.one))
  for(r in bg.one:nd.one){
    if (pan.one[r-bg.one+1] > 0.05) {
        pt.one[r-bg.one+1,] <- rep(NA,dim(allcomb)[2])
    }else{
      for(i in 1:dim(allcomb)[2]){
        pt.one[r-bg.one+1,i] <- unlist(t.test(data.hyp[data.hyp[,2]==allcomb[1,i],r], data.hyp[data.hyp[,2]==allcomb[2,i],r])[3])
        pt.corr.one[r - bg.one + 1,] <- p.adjust(pt.one[r - bg.one + 1,], method = "bonferroni")
      }
    }
  }
  
  kable(cbind(c(" ",names(data.hyp[,bg.one:nd.one])),rbind(c("CW vs CM","CW vs TM","CW vs TW","CM vs TM","CM vs TW","TM vs TW"),round(pt.corr.one,3))))
  
  # Average
  bg.avg <- 47
  nd.avg <- 68
  pt.corr.avg <- array(data=NA, dim=dim(pt.avg))
  for(r in bg.avg:nd.avg){
    if (pan.avg[r-bg.avg+1] > 0.05) {
        pt.avg[r-bg.avg+1,] <- rep(NA,dim(allcomb)[2])
    }else{
      for(i in 1:dim(allcomb)[2]){
        pt.avg[r-bg.avg+1,i] <- unlist(t.test(data.hyp[data.hyp[,2]==allcomb[1,i],r], data.hyp[data.hyp[,2]==allcomb[2,i],r])[3])
        pt.corr.avg[r - bg.avg + 1,] <- p.adjust(pt.avg[r - bg.avg + 1,], method = "bonferroni")
      }
    }
  }
  
  kable(cbind(c(" ",names(data.hyp[,bg.avg:nd.avg])),rbind(c("CW vs CM","CW vs TM","CW vs TW","CM vs TM","CM vs TW","TM vs TW"),round(pt.corr.avg,3))))
```

\newpage

## Correlations <a name="correlations"></a>
between T1 and T2
```{r corr all}
bg <- 36
nd <- 108
ln <- nd-bg+1

# Object to save correlations
corrall <- array(data=NA, dim = ln)

# Compute ANOVA for every predictor and save p-value
for(i in bg:nd){
  corrall[i-bg+1] <- cor(x = data.all[,i], y = data.all[,i + ln + 1])
}

summary(corrall)
```

```{r corr hyp}
bg.one <- 3
nd.one <- 24
ln <- nd.one-bg.one+1

# Object to save correlations
corrhyp <- array(data=NA, dim = ln)

# Compute ANOVA for every predictor and save p-value
for(i in bg.one:nd.one){
  corrhyp[i-bg.one+1] <- cor(x = data.hyp[,i], y = data.hyp[,i + ln])
}

summary(corrhyp)

# plot with correlations? Which region lies where?
```

## Discussion <a name="discussion"></a>

```{r temp, echo=FALSE}

```
